Fourmile

### 2022-09-02 fourmile_dataprocess.Rmd
filter out prism non winter months next

```{r precip, echo=F}
#daily precip
daily_p <- prec %>%
  replace(.==-9999, NA) %>%
  mutate(date = dmy(date)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date)) %>%
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))

@@

>>>>

```{r precip, echo=F}
#daily precip
prec_update <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate(Gordon_South = ifelse(!doy %in% c(152:258), 
                               NA, Gordon_South),
         Gordon_North = ifelse(!doy %in% c(152:258), 
                               NA, Gordon_North),
         GH = ifelse(!doy %in% c(152:258), 
                               NA, GH),
         LM = ifelse(!doy %in% c(152:258), 
                               NA, LM),
         SE = ifelse(!doy %in% c(152:258), 
                               NA, SE),
         SP = ifelse(!doy %in% c(152:258), 
                               NA, SP),
         ST = ifelse(!doy %in% c(152:258), 
                               NA, ST),
         NADP_SL = ifelse(!doy %in% c(152:258), 
                               NA, NADP_SL)) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), funs(lead), n = 1) #%>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), )

daily_p <- prec %>%
  replace(.==-9999, NA) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date))
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))

@@

## Compare Niwot SNOTEL pirecip to prism pixel

```{r}
niwot_prism <- read_csv(here('data', 'niwot_prism_compare.csv'))

ni_prism <- niwot_prism %>%
  filter(!row_number() %in% c(1:10)) %>%
  rename(date = 1,
         prism_mm = 2) %>%
  mutate(date = ymd(date))

niwot_snotel <- prec_update %>%
  dplyr::select(c(date, Niwot_Snotel)) %>%
  rename(snotel_mm = Niwot_Snotel)

niwot_compare <- full_join(ni_prism, niwot_snotel, by = 'date')

niwot_compare <- niwot_compare %>%
  mutate(diff_mm = snotel_mm - prism_mm) %>%
  na.omit()

#filter to look at sept - june
niwot_winter_comp <- niwot_compare %>%
  mutate(month = month(date)) %>%
  filter(!month %in% c(6:8))

summary(niwot_winter_comp)

niwot_prismshift <- niwot_compare %>%
  mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
  mutate(month = month(date)) %>%
  filter(!month %in% c(6:8)) %>%
  mutate(diff_mm = snotel_mm - prism_mm)

summary(niwot_prismshift)
